Stuff that may well go into the project report

### 2014-10-15 stuff_somewhat_organised.tex
Fortsatt møkk.

\begin{description}
	\item[Setting up an approximate problem:] We fix $T<\infty$ and consider the problem
		\begin{equation*}
			\begin{cases}
			\partial_t u_n &= \Delta\Phi_n(u_n) + f_n, \quad \text{ in } Q_T \\
			u_n(x,0) &= u_{0,n}(x),	\quad \text{ on } \overline{\Omega} \\
			u_n(x,t) &= 0, \quad \text{ on }  \partial \Omega \times (0,T).
			\end{cases}
		\end{equation*}			
	By virtue of theorem \ref{thm:classical_existence}, this approximate problem has a unique solution $u_n \in C^{2,1}(\overline{Q}_T)$.

	\item[Control of the spatial derivative:] Now we define $w_n = \Phi_n(u_n)$, multiply the GPME by $w_n$ and integrate over $Q_T$, which results in
	\begin{equation*}
	\iint_{Q_T}w_n\partial_t u_n dxdt = \iint_{Q_T}w_n\Delta w_n dxdt + \iint_{Q_T}f_n w_n dxdt.
	\end{equation*}
	Now we do exactly as we did the section on weak energy solutions and do integration by parts on the first term on the right hand side. We also notice that $w_n \partial_t u_n = \partial_t \Psi_n(u_n)$. Thus,
	\begin{equation*}
	\int_\Omega \Psi(u_n(T))dx + \iint_{Q_T}|\nabla w_n|^2dxdt = \int_\Omega \Psi_n(u_{0,n})dx + \iint_{Q_T}f_n w_n dxdt.
	\end{equation*}
	Considering the second term on the right hand side we have
	\begin{equation*}
	\iint_{Q_T}f_n w_n dxdt \leq C\iint_{Q_T}f_n^2 dxdt + \frac{1}{2}\iint_{Q_T}|\nabla w_n|^2dxdt,
	\end{equation*}
	after exactly the same argument as we did with (\ref{using_Poincare}). After putting it back
	\begin{equation*}
	\int_\Omega \Psi_n(u_n(T))dx + \frac{1}{2}\iint_{Q_T}|\nabla w_n|^2 dxdt \leq \int_\Omega \Psi(u_{0,n})dx + C\iint_{Q_T}f_n^2 dxdt,
	\end{equation*}
	and so we're getting close to a uniform bound on $\nabla w_n$ in $L^2(Q_T)$. We notice that
	\begin{equation*}
	\iint_{Q_T}f_n^2dxdt \leq \iint_{Q_T} f^2 dxdt,
	\end{equation*}
	by our assumption on the approximation. In addition
	\begin{equation*}
	\int_\Omega \Psi_n(u_{0,n})dx = \int_\Omega \left[ \int_0^{u_{0,n}(x)} \int_\mathbb{R} \left(\Phi(y)+\frac{y}{n}\right)\eta_{\frac{1}{n}}(s-y)dy ds \right] dx,
	\end{equation*}
	and $\eta_{\frac{1}{n}}(s-\cdot)$ has support in $[s-\frac{1}{n}, s + \frac{1}{n}]$. Therefore, by the monotonicity of $\Phi$, 
	\begin{equation*}
	\int_\Omega \Psi_n(u_{0,n})dx \leq \int_\Omega \left[ \int_0^{u_{0,n}(x)}\Phi \left(s+\frac{1}{n} \right)ds + \int_0^{u_{0,n}}\frac{s+\frac{1}{n}}{n}ds \right] dx,
	\end{equation*}
	which after a variable transformation yields
	\begin{align*}
	\int_\Omega \Psi_n(u_{0,n})dx &\leq \int_\Omega \left[ \int_{\frac{1}{n} }^{u_{0,n}(x) + \frac{1}{n} } \Phi(s)ds + \frac{u_{0,n}(x)^2}{2n} + \frac{u_{0,n}(x)}{n^2} \right] dx \\
	&\leq \int_\Omega \left[ \Psi\left(u_{0,n} +\frac{1}{n}\right) - \Psi\left(\frac{1}{n}\right) + \frac{1}{2n}\left(u_{0,n} + \frac{1}{n}\right)^2 \right] dx.
	\end{align*}
	Using now that $|u_{0,n}| \leq u_0$ and that $\Omega$ is a bounded set, we get a bound on this integral independent of $n$. And so $\iint_{Q_T} |\nabla w_n|^2 dxdt$ has a bound independent of $n$.
\end{description}

>>>>

\begin{description}
	\item[Setting up an approximate problem:] We fix $T<\infty$ and consider the problem
		\begin{equation}
		\label{approximate_problem}
			\begin{cases}
			\partial_t u_n &= \Delta\Phi_n(u_n) + f_n, \quad \text{ in } Q_T \\
			u_n(x,0) &= u_{0,n}(x),	\quad \text{ on } \overline{\Omega} \\
			u_n(x,t) &= 0, \quad \text{ on }  \partial \Omega \times (0,T).
			\end{cases}
		\end{equation}			
	By virtue of theorem \ref{thm:classical_existence}, this approximate problem has a unique solution $u_n \in C^{2,1}(\overline{Q}_T)$.

	\item[Control of the spatial derivative:] Now we define $w_n = \Phi_n(u_n)$, multiply the GPME by $w_n$ and integrate over $Q_T$, which results in
	\begin{equation*}
	\iint_{Q_T}w_n\partial_t u_n dxdt = \iint_{Q_T}w_n\Delta w_n dxdt + \iint_{Q_T}f_n w_n dxdt.
	\end{equation*}
	Now we do exactly as we did the section on weak energy solutions and do integration by parts on the first term on the right hand side. We also notice that $w_n \partial_t u_n = \partial_t \Psi_n(u_n)$. Thus,
	\begin{equation*}
	\int_\Omega \Psi(u_n(T))dx + \iint_{Q_T}|\nabla w_n|^2dxdt = \int_\Omega \Psi_n(u_{0,n})dx + \iint_{Q_T}f_n w_n dxdt.
	\end{equation*}
	Considering the second term on the right hand side we have
	\begin{equation*}
	\iint_{Q_T}f_n w_n dxdt \leq C\iint_{Q_T}f_n^2 dxdt + \frac{1}{2}\iint_{Q_T}|\nabla w_n|^2dxdt,
	\end{equation*}
	after exactly the same argument as we did with (\ref{using_Poincare}). After putting it back
	\begin{equation*}
	\int_\Omega \Psi_n(u_n(T))dx + \frac{1}{2}\iint_{Q_T}|\nabla w_n|^2 dxdt \leq \int_\Omega \Psi(u_{0,n})dx + C\iint_{Q_T}f_n^2 dxdt,
	\end{equation*}
	and so we're getting close to a uniform bound on $\nabla w_n$ in $L^2(Q_T)$. We notice that
	\begin{equation*}
	\iint_{Q_T}f_n^2dxdt \leq \iint_{Q_T} f^2 dxdt,
	\end{equation*}
	by our assumption on the approximation. In addition
	\begin{equation*}
	\int_\Omega \Psi_n(u_{0,n})dx = \int_\Omega \left[ \int_0^{u_{0,n}(x)} \int_\mathbb{R} \left(\Phi(y)+\frac{y}{n}\right)\eta_{\frac{1}{n}}(s-y)dy ds \right] dx,
	\end{equation*}
	and $\eta_{\frac{1}{n}}(s-\cdot)$ has support in $[s-\frac{1}{n}, s + \frac{1}{n}]$. Therefore, by the monotonicity of $\Phi$, 
	\begin{equation*}
	\int_\Omega \Psi_n(u_{0,n})dx \leq \int_\Omega \left[ \int_0^{u_{0,n}(x)}\Phi \left(s+\frac{1}{n} \right)ds + \int_0^{u_{0,n}}\frac{s+\frac{1}{n}}{n}ds \right] dx,
	\end{equation*}
	which after a variable transformation yields
	\begin{align*}
	\int_\Omega \Psi_n(u_{0,n})dx &\leq \int_\Omega \left[ \int_{\frac{1}{n} }^{u_{0,n}(x) + \frac{1}{n} } \Phi(s)ds + \frac{u_{0,n}(x)^2}{2n} + \frac{u_{0,n}(x)}{n^2} \right] dx \\
	&\leq \int_\Omega \left[ \Psi\left(u_{0,n} +\frac{1}{n}\right) - \Psi\left(\frac{1}{n}\right) + \frac{1}{2n}\left(u_{0,n} + \frac{1}{n}\right)^2 \right] dx.
	\end{align*}
	Using now that $|u_{0,n}| \leq u_0$ and that $\Omega$ is a bounded set, we get a bound on this integral independent of $n$. And so $\iint_{Q_T} |\nabla w_n|^2 dxdt$ has a bound independent of $n$.

	\item[Control of the temporal derivative:] Now we let $\zeta = \zeta(t)$ be a $C^1([0,T],[0,1])$ cutoff function so that $\zeta(0) = \zeta(T) = 1$. If we multiply (\ref{approximate_problem}) by $\zeta \partial_tw_n$ and integrate over $Q_T$ we get
	\begin{equation}
	\label{temporal_bound_start}
	\iint_{Q_T}\zeta \Phi'_n(u_n)|\partial_t u_n|^2 dxdt = \iint_{Q_T} \left\{ \zeta \partial_t w_n \Delta w_n + \zeta \partial_t w_n f_n \right\} dxdt.
	\end{equation}
	Let's start by considering the first term on the right hand side. By the product rule for the divergence
	\begin{equation*}
	\int_0^T \zeta \int_\Omega \partial_t w_n \Delta w_n dxdt = \int_0^T \zeta \int_\Omega \left\{ \nabla \cdot (\partial_t w_n \nabla w_n) - (\partial_t \nabla w_n) \cdot \nabla w_n \right\} dx dt.
	\end{equation*}
	So after using the divergence theorem together with the homogeneous boundary data, as well as noticing that $(\partial_t \nabla w_n) \cdot \nabla w_n = \frac{1}{2}\partial_t |\nabla w_n|^2$, we see that
	\begin{equation*}
	\int_0^T \zeta \int_\Omega \partial_t w_n \Delta w_n dxdt = -\iint_{Q_T}\frac{\zeta}{2}\partial_t |\nabla w_n|^2 dxdt.
	\end{equation*}
	Integrating by parts in the temporal dimension, we end up with
	\begin{equation*}
	\int_0^T \zeta \int_\Omega \partial_t w_n \Delta w_n dxdt = \iint_{Q_T} \frac{\partial_t \zeta}{2} |\nabla w_n|^2 dxdt - \frac{1}{2}\int_\Omega \left\{ |\nabla w_n(T)|^2 - |\nabla w_n(0)|^2 \right\} dx.
	\end{equation*}
	A similar inetgration by parts in the temporal dimension of the last term on the right hand side in (\ref{temporal_bound_start}) yields
	\begin{equation*}
	\iint_{Q_T} \zeta f_n \partial_t w_n dxdt = -\iint_{Q_T} \partial_t (\zeta f_n) w_n dxdt + \int_\Omega \left\{ f_n(T)w_n(T) - f_n(0)w_n(0) \right \} dx.
	\end{equation*}
	For the last term in this integral we can do the same trick as we did previously for the energy estimate. We use Cauchy-Schwarz and the inequality $\sqrt{ab} \leq \frac{c^2}{4}a + \frac{1}{c^2}b$. Then, after using a Poincaré inequality we can choose $c$ so that the integrals of $|\nabla w_n|^2$ at the temporal endpoints are cancelled. In toto we end up with
	\begin{align*}
	\iint_{Q_T} \zeta \Phi'_n(u_n) |\partial_t u_n|^2 dxdt &\leq \iint_{Q_T} \left\{ \frac{\partial_t \zeta}{2}|\nabla w_n|^2 - \partial_t(\zeta f_n) w_n \right\} dxdt \\
	&+ \frac{C}{2}\int_\Omega \left\{ f_n^2(T) - f_n^2(0) \right\} dx	\\
	&= \iint_{Q_T} \left\{ \frac{\partial_t \zeta}{2}|\nabla w_n|^2 - \partial_t(\zeta f_n) w_n \right\} dxdt \\
	&+ C \iint_{Q_T} f_n\partial_t f_n dxdt.
	\end{align*}
	Thus, by our assumption that $f$ and $\partial_t f$ are bounded, and our previous energy bound, the left hand side is bounded independent of $n$.

	In particular, we can choose $\zeta = 1$\footnote{Yikes, sorry about the kind of a fortiori argument, those are always a bit of a headache.}, and we get a bound on $\Phi'_n(u_n)|\partial_t u_n|^2$ in $L^1(Q_T)$. See now that $|\partial_t w_n	|^2 = \Phi'_n(u_n)^2|\partial_t u_n|^2$. And so, beacuse $\Phi'(u)$ is bounded for all $|u| \leq C$, we have that $\Phi'_n(u_n)$ is uniformly bounded, our latest integral bound gives us that $\partial_t w_n$ is uniformly bounded in $L^2(Q_T)$.

	\item[Using a compactness argument:] We can conclude that $\{w_n\}_{n \in \mathbb{N}}$ is a bounded sequence in $H^1(Q_T)$, so by theorem \ref{thm:Rellich} it has convergent subsequence $\{w_{n_j}\}_{j \in \mathbb{N}}$ that converges to some $w$ in $L^2(Q_T)$.

	\item[Convergence of $u_n$:] Recall that we defined $w_n = \Phi_n(u_n)$
\end{description}
